### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

\stitle{(i) Localization with pattern fragmentation}. We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
(3) $E_{fi}$ is exactly the edges in $P$ on $V_{fi}$, and (4) $C=E_P \setminus (E_{f1}\cup\ldots\cup E_{fh})$.

@@

\vspace{-0.5ex}
However, $P$ and $h$ are typically small in practice~\cite{FanLMTWW10}, \eg $|P|=15$ and $h=3$.
In light of this, we give a heuristic algorithm, denoted by \kw{PFrag}, for the problem, and is shown in the
full version~\cite{fullvldb18}.
\kw{PFrag} works by connecting pattern fragmentation to the widely studied {\sc $(k, \nu)$-Balanced Partition} problem \cite{AndreevR06},
which is not approximable in general, but has efficient and sophisticated heuristic algorithms~\cite{metis-KarypisK98a}.

\stitle{(ii) Localization with affected balls (\affballsx)}.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computing and updating match relations for all balls.

We say a ball in $G$ is {\em affected} \wrt an incremental algorithm \algorithm{A}, and pattern and data updates,
if \algorithm{A} accesses the ball again.
We use $||\affballsx||$ and $|\affballsx|$ to denote the cardinality and total size of \affballsx, respectively.

@@

\stitle{Remark}. By pattern fragmentation and affected balls, we essentially localize the impact of pattern and data updates from the entire to a fraction of $P$ and from all to a subset of balls in $G$ for team simulation.

%\vspace{-0.5ex}
\stitle{Algorithm \inc}. We now provide a unified incremental algorithm \inc  to handle both pattern and data updates.

Given $P$ with its $h$-fragmentation ${\cal P}_{h}$, $G$, two integers $k, r$,
and auxiliary structures such as the partial match relations for all pattern fragments and all balls (radius $r$),
while auxiliary structures are to be presented in next section,
the algorithm consists of three steps for $\Delta P$ and $\Delta G$, as follows.

>>>>

\stitle{(1) Localization with pattern fragmentation}. We say that \{$P_{f1}(V_{f1},V_{f1})$, $\ldots$, $P_{fh}(V_{fh},V_{fh})$, $C$\} is an {\em $h$-fragmentation} of pattern $P(V_{P}$, $E_{P})$, denoted as ${\cal P}_{h}$,
if (1) $\bigcup_{i=1}^{h}V_{fi}=V_{P}$, (2) $V_{fi}\cap V_{fj} = \emptyset$ for any $i\ne j\in[1, h]$,
(3) $E_{fi}$ is exactly the edges in $P$ on $V_{fi}$, and (4) $C=E_P \setminus (E_{f1}\cup\ldots\cup E_{fh})$.

@@

However, $P$ and $h$ are typically small in practice~\cite{FanLMTWW10}, \eg $|P|=15$ and $h=3$.
In light of this, we give a heuristic algorithm, denoted by \kw{PFrag}, for the problem, and is shown in the
full version~\cite{fullvldb18}.
\kw{PFrag} works by connecting pattern fragmentation to the widely studied {\sc $(k, \nu)$-Balanced Partition} problem \cite{AndreevR06},
which is not approximable in general, but has efficient and sophisticated heuristic algorithms~\cite{metis-KarypisK98a}.

\stitle{(2) Localization with affected balls (\affballsx)}.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computing and updating match relations for all balls.

We say that a ball in $G$ is {\em affected} \wrt an incremental algorithm \algorithm{A}, and pattern and data updates,
if \algorithm{A} accesses the ball again.
We use $||\affballsx||$ and $|\affballsx|$ to denote the cardinality and total size of \affballsx, respectively.

@@

%\stitle{Remark}. By pattern fragmentation and affected balls, we essentially localize the impact of pattern and data updates from the entire to a fraction of $P$ and from all to a subset of balls in $G$ for team simulation.

%\vspace{-0.5ex}
\stitle{(3) Algorithm \inc}. We now provide a unified incremental solution to handle both pattern and data updates.

Given pattern $P$ with its $h$-fragmentation ${\cal P}_{h}$, data graph $G$, two integers $r$ and $k$,
and auxiliary structures (to be introduced in Section \ref{sec-IncAlg}) such as the partial match relations for all pattern fragments and all balls (radius $r$),
the algorithm consists of three steps for $\Delta P$ and $\Delta G$, as follows.
